On the Origin of Shrimpoluminescence

### 2022-01-06 sonoluminescence/paper/paper.tex
sdfadsfa

A simple but reasonable model for the gas dyanmics in the bubble is that of an adiabatically, quasistatically compressed ideal gas \cite{brenner2002single} \footnote{Actually we want to study a \emph{Van der Walls} gas, but we will sneak this aspect in later.}. Let us remind ourselves what the pressure is in this case. Suppose that we have a volume, $V$, of an ideal gas containing $N$ particles at a temperature $T$. The ideal gas law tells us the equation of state is $PV=Nk_BT$ with $k_B$ \emph{Boltzmann's constant}. Since we are assuming adiabatic compression, the second law of thermodynamics tells us that $dU=-PdV$ with $U$ the internal energy in the gas. Moreover, we may use the equipartition theorem to write $dU=N f k_B dT/2$ with $f$ the number of \emph{degrees of freedom} per particle \cite{}. Recall that for an ideal gas \cite{}:
\begin{equation}
\begin{split}
    C_V &= \frac{N f k_B}{2} \\
    C_P &= C_V+N k_B \\
    \frac{C_P}{C_V} &= 1+\frac{f}{2} \equiv \Gamma 
\end{split}
\end{equation}
with $C_V$ and $C_P$ the heat capcities at constant volume and pressure respectively. For a monatomic ideal gas, $f=3$ and $\Gamma=5/2$. Now we can use the second law of thermodynamics to write $C_V dT = -P dV$. From the equation of state, we have
\begin{equation}
    dT = \frac{PdV+VdP}{Nk_B}=\frac{PdV+VdP}{C_P-C_V}.
\end{equation}
Eliminating $dT$ and simplifying, 
\begin{equation}
    \frac{dP}{P}=-\left(\frac{C_P}{C_V}\right) \frac{dV}{V} = -\Gamma \frac{dV}{V}.
    \label{eq:dP}
\end{equation}
Integrating eq. \ref{eq:dP}, we find 
\begin{equation}
    P_2 = P_1 \left(\frac{V_1}{V_2}\right)^\Gamma
\label{eq:P}
\end{equation}
where $P_2$ is the pressure in a gas at volume $V_2$ that was initially contained in a volume $V_1$ at pressure $P_1$. Importantly we have not made any assumptions about the shape of the container.

Let us now connect this to the problem of SBSL. In our case, we assume that our bubble has an \emph{ambient} radius $R_0$, leading to volume $V_0 =  4/3 \pi R_0^3$. Similarly, we will assume the pressure in the bubble at ambient radius $R_0$ is known and we will call it $p_0$. What we want to calculate is the pressure in the gas as a function of the bubble's radius $R(t)$ determined from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}). Earlier we called the pressure in the gas $p_g(t)$ and we will stick with this here. Plugging these into eq. \ref{eq:P}, (and sneaking in a modification) we arrive at a very commonly used equation in the context of SBSL \cite{brenner2002single,lofstedt1995sonoluminescing,barber1997defining,lofstedt1993toward}:
\begin{equation}
    p_g(t) = p_0 \left( \frac{R_0^3}{R^3(t)-h^3} \right)^ \Gamma
    \label{eq:p_g}
\end{equation}
The new variable $h$ that was added willy-nilly is called the \emph{Van der Walls hard-core radius} and its purpose is to make sure that, if the bubble collapses so strongly that its contents become incompressible (i.e. $R(t)\rightarrow h$), the pressure diverges \cite{lofstedt1993toward,brenner2002single}. Eq. \ref{eq:p_g} can be inserted into an RP equation which can then be integrated numerically to determine the bubble's dynamics. Now recall that one of main goals of modelling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3}{R^3(t)-h^3} \right)^ {\Gamma-1}.
    \label{eq:T(t)}
\end{equation}
Of course we still have to assign a reasonable guess to $T_0$, the temperature in the bubble at ambient radius $R_0$.

>>>>

A simple but reasonable model for the gas dyanmics in the bubble is that of an adiabatically, quasistatically compressed ideal gas \cite{brenner2002single} \footnote{Actually we want to study a \emph{Van der Walls} gas, but we will sneak this aspect in later. The modifications to the result for an ideal gas are simple.}. Let us remind ourselves what the pressure is in this case. Suppose that we have a volume, $V$, of an ideal gas containing $N$ particles at a temperature $T$. The ideal gas law tells us the equation of state is $PV=Nk_BT$ with $k_B$ \emph{Boltzmann's constant}. Since we are assuming adiabatic compression, the second law of thermodynamics tells us that $dU=-PdV$ with $U$ the internal energy in the gas. Moreover, we may use the equipartition theorem to write $dU=N f k_B dT/2$ with $f$ the number of \emph{degrees of freedom} per particle \cite{}. Recall that for an ideal gas \cite{}:
\begin{equation}
\begin{split}
    C_V &= \frac{N f k_B}{2} \\
    C_P &= C_V+N k_B \\
    \frac{C_P}{C_V} &= 1+\frac{f}{2} \equiv \Gamma 
\end{split}
\end{equation}
with $C_V$ and $C_P$ the heat capcities at constant volume and pressure respectively. For a monatomic ideal gas, $f=3$ and $\Gamma=5/2$. Now we can use the second law of thermodynamics to write $C_V dT = -P dV$. From the equation of state, we have
\begin{equation}
    dT = \frac{PdV+VdP}{Nk_B}=\frac{PdV+VdP}{C_P-C_V}.
\end{equation}
Eliminating $dT$ and simplifying, 
\begin{equation}
    \frac{dP}{P}=-\left(\frac{C_P}{C_V}\right) \frac{dV}{V} = -\Gamma \frac{dV}{V}.
    \label{eq:dP}
\end{equation}
Integrating eq. \ref{eq:dP}, we find 
\begin{equation}
    P_2 = P_1 \left(\frac{V_1}{V_2}\right)^\Gamma
\label{eq:P}
\end{equation}
where $P_2$ is the pressure in a gas at volume $V_2$ that was initially contained in a volume $V_1$ at pressure $P_1$. Importantly we have not made any assumptions about the shape of the container.

Let us now connect this to the problem of SBSL. In our case, we assume that our bubble has an \emph{ambient} radius $R_0$, leading to volume $V_0 =  4/3 \pi R_0^3$. Similarly, we will assume the pressure in the bubble at ambient radius $R_0$ is known and we will call it $p_0$. What we want to calculate is the pressure in the gas as a function of the bubble's radius $R(t)$ determined from the RP equations (eq. \ref{eq:RP_2} or eq. \ref{eq:RP_3}). Earlier we called the pressure in the gas $p_g(t)$ and we will stick with this here. Plugging these into eq. \ref{eq:P}, (and sneaking in a modification) we arrive at a very commonly used equation in the context of SBSL \cite{brenner2002single,lofstedt1995sonoluminescing,barber1997defining,lofstedt1993toward}:
\begin{equation}
    p_g(t) = p_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ \Gamma
    \label{eq:p_g}
\end{equation}
The new variable $h$ that was added willy-nilly is called the \emph{Van der Walls hard-core radius} and its purpose is to make sure that, if the bubble collapses so strongly that its contents become incompressible (i.e. $R(t)\rightarrow h$), the pressure diverges \cite{lofstedt1993toward,brenner2002single}. Eq. \ref{eq:p_g} can be inserted into an RP equation which can then be integrated numerically to determine the bubble's dynamics. Now recall that one of main goals of modelling the bubble dynamics in SBSL was to calculate the temperature inside the bubble in order to model the light emission. Following similar steps to deriving $p_g(t)$, we can write down an equation for the temperature $T$ \cite{barber1997defining,brenner2002single}:
\begin{equation}
    T(t) = T_0 \left( \frac{R_0^3-h^3}{R^3(t)-h^3} \right)^ {\Gamma-1}.
    \label{eq:T(t)}
\end{equation}
Of course we still have to assign a reasonable guess to $T_0$, the temperature in the bubble at ambient radius $R_0$.
